Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area.

### 2022-07-07 outputs/paper/paper.qmd
Update paper.qmd

@@

-   Maximum temperature

-   Minimum temperature

-   Mean temperature.

@@

-   Mean level of pollution each day

@@

>>>>

-   City

-   Maximum Temperature

-   Minimum Temperature

-   Mean Temperature

@@

@@

-   City

-   Mean pollution for pollutant each day

@@

*Temperature data*

The data for temperature was processed using R studio and R. I started off by renaming the column names for each temperature data set from 2002 to 2022. Once this was done I combined the 2002 to 2022 temperature data together. The data set initially contained 31 variables. From these I selected the city, date, year, month, day, maximum temperature, minimum temperature, and mean temperature using the dplyr package. I then cleaned the names of the data set using the janitor package. I added a column for the names of the month by mutating the data set and changed the city rows to represent only Toronto data. From here, I dropped any NA values from the maximum, minimum, and mean temperature columns. Lastly, I saved the cleaned data into the repository as a csv file.

*Pollution Data*
